Web Service Wrapping, Discovery and Consumption --- More Power to the End-User

### 2010-06-14 trunk/papers/icsoc2010/paper_sec_introduction.tex
bib changed
git-svn-id: https://svn.forge.morfeo-project.org/fast-fp7project@857 d8b0c59b-6544-0410-94d9-83a5658a058e

The remainder of this paper is organised as follows. Section 2 covers the state of the art in web services publication, discovery and wrapping/consumption. In Section 4 we present how we tackle with the web services wrapping, available possibilities and limitations. Next, section 3 describes our platform for publishing web services and empowering end-users to discover services. Section 5 gives the reader a clearer use case and how this work is integrated into the FAST platform, and finally, we present our main conclusions and highlight future lines of research in Section 6.

>>>>

The remainder of this paper is organised as follows. Section 2 covers the state of the art in web services publication, discovery and wrapping/consumption. In Section 4 we present how we tackle with the web services wrapping, available possibilities and limitations. Next, section 3 describes our platform for publishing web services and empowering end-users to discover services. Section~\ref{sec:use_case} gives the reader a clearer use case and how this work is integrated into the FAST platform, and finally, we present our main conclusions and highlight future lines of research in Section 6.

### 2010-06-14 trunk/papers/icsoc2010/paper_sec_use_case.tex
bib changed
git-svn-id: https://svn.forge.morfeo-project.org/fast-fp7project@857 d8b0c59b-6544-0410-94d9-83a5658a058e

The two artifacts presented in this paper may be deployed and used separately by third-party applications. The intention was to show the advances made regarding web service discovery and consumption. However, they were developed in order to be part of the FAST platform. FAST constitutes a novel approach to application composition and business process definition from a top-down user-centric perspective. Therefore, it is aimed to allow users to create their own applications by combining different components, or building blocks, such as graphical forms and back-end services in terms of their inputs and outputs. These two components, as described in Section 3 and 4, are fully integrated and present a high cohesion the rest of the components of the FAST architecture (see Picture~\ref{pic:fast_architecture}.

>>>>

The intention of this paper was to show the advances made regarding web service discovery and consumption through the two artifacts developed as part of our research. While these artifacts may be deployed and used separately by third-party applications, they were originally developed to form the backbone of the FAST platform. FAST constitutes a novel approach to application composition and business process definition from a top-down user-centric perspective. Therefore, it is aimed to allow users to create their own applications by combining different components, or building blocks, such as graphical forms and back-end services in terms of their inputs and outputs. These two components, as described in Section 3 and 4, are fully integrated and present a high cohesion the rest of the components of the FAST architecture (see Picture~\ref{pic:fast_architecture}.
